---
classoption: "runningheads"
title: "Contribution Title\\thanks{Supported by organization x.}"
shorttitle: "Short title"
# If the paper title is too long for the 
# running head, you can set an abbreviated 
# paper title here.
# shorttitle: "Abbreviated paper title"
authors: 
  - name: "First Author"
    inst: "1"
    orcid: "0000-1111-2222-3333"
  - name: "Second Author"
    inst: "2,3"
    orcid: "1111-2222-3333-4444"
  - name: "Third Author"
    inst: "3"
    orcid: "2222--3333-4444-5555"
# First names are abbreviated in the running head.
# If there are more than two authors, 'et al.' is used.
authorrunning: "F. Author et al." 
institutes: 
  - name: "Princeton University, Princeton NJ 08544, USA"
  - name: "Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany"
    email: "lncs@springer.com"
    url: "http://www.springer.com/gp/computer-science/lncs"
  - name: "ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany"
    email: "dummy@uni-heidelberg.de"
abstract: | 
  The abstract should briefly summarize the contents of the paper in 150--250 words.
keywords: 
* Beer
* supply chain
* datasets
bibliography: lncs-test.bib
# Use csl when using default citation_package for Pandoc citeproc
csl: https://www.zotero.org/styles/springer-lecture-notes-in-computer-science
# citations with arabic numbers is prefered when using natbib
natbiboptions: numbers

output: 
  rticles::lncs_article:
    citation_package: default # or natbib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.extra = "")  # This forces knitr to label all figures.
```

# Introducción
Breve descripción del problema que se analizará

## Estado del arte

Realizamos una busqueda en google académico con las siguientes palabras clave:

* beer supply chain datasets
* supply chain
* datasets

El resultado nos dio 24500 artículos

De la revisión de los más interesantes seleccionamos por la lectura del título solamente los siguientes artículos

* Carbonneau, R., Laframboise, K., & Vahidov, R. (2008). Application of machine learning techniques for supply chain demand forecasting. European Journal of Operational Research, 184(3), 1140-1154.

* Fu, G., Shen, S., Zhao, L., Liu, Q., & Li, W. (2013, December). Effective tracking and tracing in rfid-enabled supply chain networks. In Proceedings 2013 International Conference on Mechatronic Sciences, Electric Engineering and Computer (MEC) (pp. 2310-2315). IEEE.

* Mircetic, D., Rostami-Tabar, B., Nikolicic, S., & Maslaric, M. (2022). Forecasting hierarchical time series in supply chains: an empirical investigation. International Journal of Production Research, 60(8), 2514-2533.

Impresión de cada artículo.

Luego de haber revisado estos artículos hemos incluido las siguientes palabras a las palabras claves:

* beer supply chain datasets
* supply chain
* datasets
* Neural net

## Autores más destacados

## Justificación 

del trabajo que haremos

# Materiales y Métodos

## Materiales

escribir algo sobre el dataset, el trabajo que se hizo, si faltaban datos, todos los arreglos.

escribir sobre el método de normalización

Hacer el análisis exploratorio

```{r}
summary(cars)

```
```{r}
plot(Titanic)

```
```{r}
plot(iris)

```


## Métodos

El dataset que utilizamos podría ser analizado con KNN o también con una red neuronal, se podrian clasificar los consumos por mes, etc.

Considerando la estructura del dataset que conseguimos hemos optamos por utilizar el método ARIMA (copiar y pegar todo lo que hay en el archivo RMD de ARIMA)

# Caso de Estudio

# Interpretación de resultados y conclusiones


## A Subsection Sample

Please note that the first paragraph of a section or subsection is not indented. 
The first paragraph that follows a table, figure, equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

### Sample Heading (Third Level)

Only two levels of headings should be numbered. 
Lower level headings remain unnumbered; they are formatted as run-in headings.

#### Sample Heading (Fourth Level)

The contribution should contain no more than four levels of headings. 
Table\ \ref{tab:table} gives a summary of all heading levels.

```{r table}
knitr::kable(head(pressure), 
             format = "latex",
             caption = "Table captions should be placed above the tables.")
```

\noindent Displayed equations are centered and set on a separate line.

\begin{equation}
x + y = z
\end{equation}

Please try to avoid rasterized images for line-art diagrams and schemas. 
Whenever possible, use vector graphics instead (see Fig.\ \ref{fig:fig1}).

```{r fig1, fig.cap = "A figure caption is always placed below the illustration. Please note that short captions are centered, while long ones are justified by the macro package automatically."}
plot(pressure)
```

::: {.theorem latex=true}
This is a sample theorem. The run-in heading is set in bold, while the following text appears in italics. Definitions, lemmas, propositions, and corollaries are styled the same way.
:::

The environments 'definition', 'lemma', 'proposition', 'corollary', 'remark', and 'example' are defined in the LLNCS documentclass as well.

::: {.proof latex=true}
Proofs, examples, and remarks have the initial word in italics, while the following text appears in normal font.
:::

For citations of references, use\ \cite{Nuncio2011}.
Multiple citations are grouped\ \cite{Levitus2012,Raphael2004}.

### Acknowledgements
Please place your acknowledgments at the end of the paper, preceded by an unnumbered run-in heading (i.e. 3rd-level heading).
