---
title: Cadena de suministros de la cerveza en Australia
author:
  - name: Gustavo Jemio
    affil: 1,\ddagger,*
  - name: Scarlen Lobaton
    affil: 2, \dagger, \ddagger
  - name: Noelia Baina
    affil: 3, \dagger, \ddagger
  - name: Alejandra Rubin de Celis
    affil: 4, \dagger, \ddagger
affiliation:
  - num: 1
    address: |
      Laboratorios Cofar S.A. 
      Producción, Líquidos Estériles
      Calle Victor Eduardo, Zona Miraflores. # 2293, La Paz, Bolivia.
    email: gus.jemio@gmail.com
  - num: 2
    address: |
      Cossmil
      Av. Camacho, # 1324. La Paz, Bolivia.
    email: calen1297@gmail.com
  - num: 3
    address: |
      Universidad Catolica Boliviana "SAN PABLO"
      Estudiante
      Av. 14 de septiembre, # 4807, Zona obrajes, La Paz, Bolivia.
    email: noebel231196@gmail.com
  - num: 4
    address: |
      Centro de distribución El Alto CBN 
      Logistica
      Av. 6 de marzo, El Alto, Bolivia.
    email: alerubindecelisr@gmail.com
# author citation list in chicago format
authorcitation: |
  Leutnant, D.; Doe, J.
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  gus.jemio@gmail.com; Tel.: +591-777-93-966.
# document options
journal: Iberoamerican journal of industrial engineering
type: article
status: submit
# front matter
simplesummary: |
  A Simple summary goes here.
abstract: |
  Arima is a very popular model for scenario simulation and forecasting for technology-based companies, it is flexible and ideal for working with models with seasonal variations based on historical data information that is not related to the innovative product, but is complementary or substitute. Especially to make predictions on future scenarios.
  In this article we perform the applicability of the ARIMA method to obtain a time series forecast based on beer demand datasets in Australia.
  Our results suggest that the ARIMA model parameters can be used as a predictive model to forecast future values of time series.
  By adjusting the ARIMA model, the study shows that the demand for beer shows continuous growth without finding negative deviations that could impact future forecasts.
  
  Arima es modelo muy popular para simulado y pronóstico de escenarios para empresas de base tecnológica, es flexible e ideal para trabajar modelos con variaciones estacionales a partir de información histórica de datos que no son relativos al producto innovador, pero que sí son complementarios o sustitutos. Especialmente para hacer predicciones en los escenarios futuros. 
  En este artículo realizamos la aplicabilidad del método ARIMA para obtener un pronóstico de series temporales en base a datasets de la demanda de cerveza en Australia.
  Nuestros resultados sugieren que los parámetros del modelo ARIMA se pueden usar como un modelo predictivo para hacer pronósticos de valores futuros de las series temporales
  Al ajustar el modelo ARIMA, el estudio demuestra que la demanda de cerveza muestra un crecimiento continuo sin encontrar desviaciones negativas que puedan impactar los pronósticos futuros.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
funding: |
  Please add: ``This research received no external funding'' or ``This research 
  was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded 
  by XXX''. Check carefully that the details given are accurate and use the 
  standard spelling of funding agency names at 
  \url{https://search.crossref.org/funding}, any errors may affect your future 
  funding.
institutionalreview: |
  In this section, you should add the Institutional Review Board Statement and 
  approval number, if relevant to your study. You might choose to exclude 
  this statement if the study did not require ethical approval. Please note 
  that the Editorial Office might ask you for further information. Please add 
  “The study was conducted in accordance with the Declaration of Helsinki, 
  and approved by the Institutional Review Board (or Ethics Committee) of 
  NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies 
  involving humans. OR “The animal study protocol was approved by the 
  Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE 
  (protocol code XXX and date of approval).” for studies involving animals. 
  OR “Ethical review and approval were waived for this study due to REASON 
  (please provide a detailed justification).” OR “Not applicable” for
   studies not involving humans or animals.
informedconsent: |
  Any research article describing a study involving humans should contain this 
  statement. Please add ``Informed consent was obtained from all subjects 
  involved in the study.'' OR ``Patient consent was waived due to REASON 
  (please provide a detailed justification).'' OR ``Not applicable'' for 
  studies not involving humans. You might also choose to exclude this statement 
  if the study did not involve humans.
  
  Written informed consent for publication must be obtained from participating 
  patients who can be identified (including by the patients themselves). Please 
  state ``Written informed consent has been obtained from the patient(s) to 
  publish this paper'' if applicable.
dataavailability: |
  We encourage all authors of articles published in MDPI journals to share 
  their research data. In this section, please provide details regarding where 
  data supporting reported results can be found, including links to publicly 
  archived datasets analyzed or generated during the study. Where no new data 
  were created, or where data is unavailable due to privacy or ethical 
  re-strictions, a statement is still required. Suggested Data Availability 
  Statements are available in section “MDPI Research Data Policies” at 
  \url{https://www.mdpi.com/ethics}.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
supplementary: |
 The following supporting information can be downloaded at:  
 \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
bibliography: mybibfile.bib
appendix: appendix.tex
endnotes: false
output: 
  rticles::mdpi_article:
    extra_dependencies: longtable
---

# Version

This Rmd-skeleton uses the mdpi Latex template published 2023-03-25. 
However, the official template gets more frequently updated than the **rticles**
package. Therefore, please make sure prior to paper submission, that you're 
using the most recent .cls, .tex and .bst files 
(available [here](http://www.mdpi.com/authors/latex)).

# Article Header Information

The YAML header includes information needed mainly for formatting the front and 
back matter of the article. Required elements include:

Journal options are in Table \ref{tab:mdpinames}. The `status` variable should 
generally not be changed by authors. The `type` variable describes 
the type of of submission and defaults to `article` but can be replaced with any of the ones in Table \ref{tab:mdpitype}

```{r mdpitype, echo = FALSE}
type <- c("abstract, addendum, article, book, bookreview, briefreport, 
casereport, comment, commentary, communication, conferenceproceedings, 
correction, conferencereport, entry, expressionofconcern, extendedabstract, 
datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, 
obituary, opinion, projectreport, reply, retraction, review, perspective, 
protocol, shortnote, studyprotocol, systematicreview, supfile, 
technicalnote, viewpoint, guidelines, registeredreport, tutorial")
knitr::kable(rticles::string_to_table(type, 3), 
             col.names = NULL, format = "latex", booktab = TRUE, 
             caption = "MDPI article types.")
```

## Journal Specific YAML variables

```yaml
# for journal Diversity,
# add the Life Science Identifier using:
lsid: http://zoobank.org/urn:lsid:zoobank.org:act:nnnn


# for journal Applied Sciences
# add featured application
featuredapplication: |
  Authors are encouraged to provide a concise 
  description of the specific application or 
  a potential application of the work. This 
  section is not mandatory.

# for the journal Data
# add dataset doi and license
dataset: https://doi.org/10.1000/182
datasetlicense: CC-BY-4.0

# for the journal Toxins
# add key contributions
keycontributions: |
  The breakthroughs or highlights of the manuscript. 
  Authors can write one or two sentences to describe 
  the most important part of the paper.

# for the journal Encyclopedia
encyclopediadef: |
  For entry manuscripts only: please provide a brief overview
  of the entry title instead of an abstract.
entrylink: The Link to this entry published on the encyclopedia platform.

# for the journal Advances in Respiratory Medicine
# add highlights
addhighlights: |
  This is an obligatory section in “Advances in Respiratory Medicine”, 
  whose goal is to increase the discoverability and readability of the
  article via search engines and other scholars. Highlights should not 
  be a copy of the abstract, but a simple text allowing the reader to 
  quickly and simplified find out what the article is about and what can 
  be cited from it. Each of these parts should be devoted up to 2~bullet 
  points.

```


\startlandscape
```{r, mdpinames, echo=FALSE, results='asis'}
mdpi_journals <- "acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis"

knitr::kable(rticles::string_to_table(mdpi_journals, 8),
             col.names = NULL,
             format = "latex",
             booktabs = TRUE, 
             caption = "MDPI journal names.",
             longtable = TRUE)

```
\finishlandscape

# Introduction

Se estudiará el caso de un producto con fuerte demanda estacional. En nuestro caso la demanda de cerveza en Australia.

Se comenzará modelando los datos de una serie temporal. Usando R, convertiremos los datos disponibles en formato de datos de serie temporal.

ARIMA es una técnica básica para el pronóstico de series de tiempo complejas, basado en inteligencia artificial. Si son series estacionales se usa S-ARIMA (Seasonal). Este artículo provee una descripción paso a paso para hacer el ajuste y parametrización de la biblioteca arima usando R.


## Estado del arte

Realizamos una busqueda en google académico con las siguientes palabras clave:

* beer supply chain datasets
* supply chain
* datasets

El resultado nos dio 24500 artículos

De la revisión de los más interesantes seleccionamos por la lectura del título solamente los siguientes artículos

Carbonneau, R., Laframboise, K., & Vahidov, R. (2008). Application of machine learning techniques for supply chain demand forecasting. European Journal of Operational Research, 184(3), 1140-1154.

Fu, G., Shen, S., Zhao, L., Liu, Q., & Li, W. (2013, December). Effective tracking and tracing in rfid-enabled supply chain networks. In Proceedings 2013 International Conference on Mechatronic Sciences, Electric Engineering and Computer (MEC) (pp. 2310-2315). IEEE.

Mircetic, D., Rostami-Tabar, B., Nikolicic, S., & Maslaric, M. (2022). Forecasting hierarchical time series in supply chains: an empirical investigation. International Journal of Production Research, 60(8), 2514-2533.

Luego de haber revisado estos artículos hemos incluido las siguientes palabras a las palabras claves:

* beer supply chain datasets
* supply chain
* datasets
* Neural net

Al revisar los artículos destacados podemos comentar lo siguiente de cada uno de ellos:

# Application of machine learning techniques for supply chain demand forecasting
Este artículo hace referencia a la investigación de la aplicabilidad de la tecnología avanzada en técnicas de aprendizaje automático, incluidas redes neuronales, redes neuronales recurrentes y máquinas de vectores de soporte, para pronosticar una demanda distorsionada al final de una cadena de suministro (efecto látigo). Los hallazgos sugieren que, si bien las redes neuronales recurrentes y las máquinas de vectores de soporte muestran el mejor rendimiento, la precisión del pronóstico no fue estadísticamente significativamente mejor que la del modelo de regresión

#Effective tracking and tracing in rfid-enabled supply chain networks
Este artículo hace referencia a que una red de cadena de suministro habilitada para RFID facilita el rastreo y seguimiento de etiquetas mediante el intercambio de datos en infraestructuras de servicios de información (IS) o servicios de descubrimiento (DS), a lo largo de todo el ciclo de vida de una etiqueta. EPCGlobal es un estándar ampliamente aplicado para una red de cadena de suministro habilitada para RFID, que define la gestión del ciclo de vida de una etiqueta EPC, al describir los problemas de seguimiento y rastreo en una red EPCGlobal. Sin embargo, los algoritmos de rastreo y rastreo existentes no consideran eventos complicados definidos en los estándares EPCGlobal, como agregación, desagregación, recuperación, comentario, etc. y rastreo en el contexto de eventos complicados.


#Forecasting hierarchical time series in supply chains: an empirical investigation
En este artículo, se investiga el desempeño de los pronóstico de combinación óptima, ascendente y descendente en una cadena de suministro. Primero se evalua su rendimiento mediante un estudio de simulación y una investigación empírica en una red de distribución. Luego, se examina la precisión del pronóstico de combinar pronósticos de estos enfoques. Los resultados revelan que las combinaciones de pronósticos producen pronósticos que son más precisos y menos sesgados que los enfoques individuales.


## Justificación

Realizamos este trabajo para poder conocer más el método ARIMA, ya que es un modelo predictivo que permite hacer pronósticos de valores futuros de las series temporales, por esta razón, como la cerveza tiene etapas en las que su venta varía, se realizó el análisis y la implementación de este método.


# Materiales y Metodos

## Materiales

Se utilizó el dataset de un caso de productos con fuerte demanda estacional. Se analizará el caso la demanda de cerveza en Australia.

Para llevar a cabo este trabajo se utilizará el método ARIMA.
ARIMA por sus siglas en inglés , acrónimo del inglés autoregressive integrated moving average , o Modelo autorregresivo integrado de media móvil es muy utilizado en estadística y econometría, en particular en series temporales, un modelo autorregresivo integrado de promedio móvil o simplemente un sistema que se comporta como ARIMA es un modelo estadístico que utiliza variaciones y regresiones de datos estadísticos con el fin de encontrar patrones para una predicción hacia el futuro.

Para llevar a cabo este trabajo se utilizaron los siguientes comandos:


```{r}
summary(cars)

```
```{r}
plot(iris)

```
## Métodos

El dataset que utilizamos podría ser analizado con KNN o también con una red neuronal, se podrian clasificar los consumos por mes, etc.

Considerando la estructura del dataset que conseguimos hemos optamos por utilizar el método ARIMA

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Consumo de cerveza

Primer paso recuperar los datos

```{r}
RawData=scan('https://themys.sid.uncu.edu.ar/~rpalma/R-cran/Routers.txt')
plot(RawData)
```

```{r}
RawData=scan('https://themys.sid.uncu.edu.ar/~rpalma/R-cran/Routers.txt')
plot(RawData, type = "l")
```


```{r}
tsData = ts(RawData, start = c(2006,1), frequency = 12)
print(tsData)
```

```{r}
plot(tsData)
```

```{r}
componentes.ts = decompose(tsData)
plot(componentes.ts)
```

```{r}
library("fUnitRoots")
urkpssTest(tsData, type = c("tau"), lags = c("short"),use.lag = NULL, doplot = TRUE)
```

```{r}
tsstationary = diff(tsData, differences=1)
plot(tsstationary)
```

```{r}
acf(tsstationary, lag.max=140)
```

```{r}
fitARIMA <- arima(tsData, order=c(1,1,1),seasonal =list(order = c(1,0,0), period = 12),method="ML")
#install.packages("lmtest")
library(lmtest)
```

```{r}
coeftest(fitARIMA)
```

```{r}
fitARIMA <- arima(tsData, order=c(1,1,1), seasonal =list(order = c(1,0,0), period = 12),method="ML")
```

```{r}
confint(fitARIMA)
```

```{r}
library(forecast)
auto.arima(tsData, trace=TRUE)
```

```{r}
predict(fitARIMA,n.ahead = 25)
```

```{r}
futurVal <- forecast(fitARIMA,h=10, level=c(82.5))
plot(futurVal)
```

```{r}
summary(tsData)

```

```{r}
boxplot(tsData)

```

```{r}
hist(tsData, main = "Histograma")

```

# Interpretación de resultados y concluciones

Según los resultados obtenidos, se utilizó R para convertir los datos en formato de datos de serie temporal, para poder tener una mejor visualización de los datos, se ajusto el primer gráfico (RawData).

Se puede observar que a inicios de la gestión 2009 y a finales de la gestión 2010 la demanda de la cerveza en Australia sufrió dos bajones en su consumo.

La demanda de la cerveza en Australia comienza con mucha variabilidad y no presenta un patrón al inicio de los datos obtenidos, posteriormente, al realizar los ajustes correspondientes se puede llegar a observar la estacionalidad de los datos, que se van ajustando.

Por otra parte, al realizar el ajuste del modelo se puede observar que el crecimiento de la demanda de cerveza va incrementando y no se genera ninguna eventualidad negativa, que pueda afectar a la demanda en el pronóstico realizado.

Los pronósticos se muestran con una linea azul, con los intervalos de predicción del 82.5% como un área sombreada oscura, y los intervalos de predicción del 95% como un área sombreada clara.


## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Bulleted lists look like this:

* First bullet
* Second bullet
* Third bullet

Numbered lists can be added as follows:

1. First item
2. Second item
3. Third item

The text continues here.

## Figures, Tables and Schemes

All figures and tables should be cited in the main text as Figure \ref{fig:fig1}, 
\ref{tab:tab1}, etc. To get cross-reference to figure generated by R chunks 
include the `\\label{}` tag in the `fig.cap` attribute of the R chunk: 
`fig.cap = "Fancy Caption\\label{fig:plot}"`.

```{r fig1, echo=FALSE, fig.width=3, fig.cap="A figure added with a code chunk.\\label{fig:fig1}"}
x = rnorm(10)
y = rnorm(10)
plot(x, y)
```


When making tables using `kable`, it is suggested to use
the `format="latex"` and `tabl.envir="table"` arguments
to ensure table numbering and compatibility with the mdpi
document class.

```{r tab1, echo=FALSE}
knitr::kable(mtcars[1:5, 1:3], format = "latex", 
             booktabs = TRUE, 
             caption = "This is a table caption. Tables should be placed in the 
             main text near to the first time they are~cited.", 
             align = 'ccc', centering = FALSE,
             table.envir = "table", position = "H")
```



For a very wide table, landscape layouts are allowed.


\startlandscape

```{r tab2, echo=FALSE}
df <- data.frame(`Title 1` = c("Entry 1", "Entry 2"),
                 `Title 2` = c("Data", "Data"),
                 `Title 3` = c("Data", "Data"),
                 `Title 4` = c("This cell has some longer content that runs over
                               two lines",
                               "Data"))
knitr::kable(df, format = "latex", 
             booktabs = TRUE, 
             caption = "This is a very wide table", 
             align = 'ccc', centering = FALSE,
             table.envir = "table", position = "H")
```

\finishlandscape

## Formatting of Mathematical Components

This is an example of an equation:

$$
a = 1.
$$

If you want numbered equations use Latex and wrap in the equation environment:

\begin{equation}
a = 1,
\end{equation}

the text following an equation need not be a new paragraph. Please punctuate 
equations as regular text.

```{comment}
If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
```

This is the example 2 of equation:

\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + 
u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

Theorem-type environments (including propositions, lemmas, corollaries etc.) 
can be formatted as follows:

Example of a theorem:

::: {.Theorem latex=true}
Example text of a theorem
:::

The text continues here. Proofs must be formatted as follows:

Example of a proof:

::: {.proof latex="[Proof of Theorem1]"}
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is 
clear which theorem is being referred to.
:::

The text continues here.

# Discussion

Authors should discuss the results and how they can be interpreted in 
perspective of previous studies and of the working hypotheses. The findings and 
their implications should be discussed in the broadest context possible. Future 
research directions may also be highlighted.

# Conclusion

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

# Patents

This section is not mandatory, but may be added if there are patents resulting
from the work reported in this manuscript.
